Adapting toolmark based chumbley score to bullets

### 2017-09-25 doc/aboutme.Rmd
update

The classification rates corresponding to the p-values where the rows correspond to the known status of the tool marks and columns represent the model conclusion. Of 50 pairs of known matching marks, we misclassified three pairs as nonmatches for false-negative error rate of 6% and 0 pairs of known nonmatching tool marks were identified as being matches
```{r cars, echo=FALSE}
a<- matrix(NA, ncol = 3, nrow = 2)
toolmark.falsepositive<- data.frame(a)
colnames(toolmark.falsepositive)<- c("Classification", "Match", "Non-Match")
toolmark.falsepositive$Classification<- c("Match", "Non-Match")
toolmark.falsepositive$Match<- c(47,0)
toolmark.falsepositive$`Non-Match`<- c(3,50)
toolmark.falsepositive

@@

Bullet signatures are chosen by
1. Filtering out Land_id for Profiles from the Hamby 44 and Hamby 252 data and removing 
all NA values
2. run_id = 3 is chosen, Seems like the signatures generated from this run_id give the closest
match. Different run_id's have some different settings for generating the signatures
(The level of smoothing does not seem to be one of them)
3. The bullet signatures when generated already included the LOESS smoothing
## Including Plots

@@

```{r echo=FALSE}
#library(tidyverse)
#install.packages("tidyverse")
falspostive<- function(sig_alpha){
  library(dplyr)
  if(is.null(all)){
    files <- dir("././data", pattern="csv")
    all <- data.frame()
    for (file in files) {
      tmp <- read.csv(file=file.path(path="././data", file)) 
      if (length(grep("x",names(tmp)) > 0)) tmp <- tmp %>% select(-x)
      all <- rbind(all, tmp)
    }
  }
    summ <- all %>% filter(!is.na(p_value)) %>%
      mutate(signif = p_value < sig_alpha) %>%
      group_by(wv, wo, match, signif) %>% tally()
    summ$error <- with(summ, match != signif)
    rates <- summ %>% group_by(wv, wo, match) %>% summarize(
      rate = n[error==TRUE]/sum(n)
    )
    combo<- list(summ, rates)
    names(combo)<- c("summ", "rates")
    return(combo)
}

a<- falspostive(0.05)

a$summ %>% ggplot(aes( x  = factor(wv), weight = n, fill=error)) + geom_bar(position="fill") +
      facet_grid(match~wo, labeller="label_both")
a$rates %>% ggplot(aes(x = wv, y = rate)) + geom_point() + facet_grid(match~wo, labeller="label_both") +  geom_line()
```

>>>>

The classification rates corresponding to the p-values where the rows correspond to the known status of the tool marks and columns represent the model conclusion. Of 50 pairs of known matching marks, we misclassified three pairs as nonmatches for false-negative error rate of 6% and 0 pairs of known nonmatching tool marks were identified as being matches.

Null Hypothesis: The toolmarks were not made by the same tool.
Alternate: Toolmarks made by the same tool.
```{r cars, echo=FALSE}
a<- matrix(NA, ncol = 3, nrow = 2)
toolmark.falsepositive<- data.frame(a)
colnames(toolmark.falsepositive)<- c("Classification", "Match", "Non-Match")
toolmark.falsepositive$Classification<- c("Match", "Non-Match")
toolmark.falsepositive$Match<- c(47,0)
toolmark.falsepositive$`Non-Match`<- c(3,50)
toolmark.falsepositive

@@

Bullet signatures are chosen by
1. Filtering out Land_id for Profiles from the Hamby 44 and Hamby 252 data and removing 
all NA values
2. run_id = 3 is chosen, Seems like the signatures generated from this run_id give the closest
match. Different run_id's have some different settings for generating the signatures
(The level of smoothing does not seem to be one of them)

The bullet signatures when generated already included the LOWESS smoothing.
Therefore, the coarseness factor is set to 1 while running the chumbley_non_random()
which generates the same_shift, different_shift, U-Stat and P_value parameters.

## Including Plots

@@

```{r echo=FALSE}
